Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-28 index.Rmd
Update metadata in index.Rmd and add files

---
title: "Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis."
author: "Paul Melloy, Emerson Del Ponte, Charles T. Gray and Adam H. Sparks"
date: "`r Sys.Date()`"
output:
  bookdown::html_book:
    theme: united
---

>>>>

---
title: "Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis."
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: 
biblio-style: apalike
link-citations: yes
github-repo: OpenPlantPathology/Mungbean_PM
description: "A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew."
---
